*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-07 Code/Manuscript_O2.Rmd
Fixed figure cap for OPP figures stating what grey and black mean more clearly

CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P. marinus* MED4 annotated with solid black circles), LLI (*P. marinus* NATL2A annotated with solid black circles), LLII/III (*P. marinus* SS120 annotated with solid black circles) and LLIV (*P. marinus* MIT9313 annotated with solid black circles).",
                       "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                       "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A,B,C) or blue (D,E,F) peak PAR and photoperiod. Under 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)D shows MIT9313 achieves fastest growth rates between blue peak PAR of 30 µmol photons m^-2^ s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h, indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^ percentile of achieved growth rates. Figure \@ref(fig:MIT9313GAM)D also shows that growth rate increases with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^.  In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods. Figure \@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels and most photoperiods with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ PAR.F igure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.  Thus the designation of MIT9313 as a LL clade is dependent upon [O~2~] and light spectra. (Figure \@ref(fig:MIT9313GAM)E).

@@

CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P. marinus* MED4 annotated with solid black circles), LLI (*P. marinus* NATL2A annotated with solid black circles), LLII/III (*P. marinus* SS120 annotated with solid black circles) and LLIV (*P. marinus* MIT9313 annotated with solid black circles).",
                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for [O~2~] (µM).",
                       "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

>>>>

CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P. marinus* MED4 protein detection annotated as solid black circles), LLI (*P. marinus* NATL2A protein detection annotated as solid black circles), LLII/III (*P. marinus* SS120 protein detection annotated as solid black circles) and LLIV (*P. marinus* MIT9313 protein detection annotated as solid black circles).",
                       "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                       "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A,B,C) or blue (D,E,F) peak PAR and photoperiod. Under 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)D shows MIT9313 achieves fastest growth rates between blue peak PAR of 30 µmol photons m^-2^ s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h, indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^ percentile of achieved growth rates. Figure \@ref(fig:MIT9313GAM)D also shows that growth rate increases with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^.  In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods. Figure \@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels and most photoperiods with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Figure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.  Thus the designation of MIT9313 as a LL clade is dependent upon [O~2~] and light spectra. (Figure \@ref(fig:MIT9313GAM)E).

@@

CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P. marinus* MED4 protein detection annotated as solid black circles), LLI (*P. marinus* NATL2A protein detection annotated as solid black circles), LLII/III (*P. marinus* SS120 protein detection annotated as solid black circles) and LLIV (*P. marinus* MIT9313 protein detection annotated as solid black circles).",
                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for [O~2~] (µM).",
                       "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")
